The effect of common network problems on students academic performance in an elearning-Environment \thanks{Supported by Goethe University Frankfurt a. Main}

### 2021-07-08 Addition.tex

\section{Discussion}
As we can see, the results show not much significance under our circumstances. Even though we cannot see a significance, we can see slight worsening of the average scores in the error groups than to the control group. But we don't have to forget, that this was a short term test (for example 1 hour exam) and we didn't include that many variables like time, age and so on. Having such problem-infected websites and platforms can be very frustrating in the long run and may make the decline of performance much worse, than we've seen here in our scenario of having to enter the 'exam' one time only.  Unfortunately, we couldn't recreate the long-term-scenario due to its complexity and sheer number of variables.          
\section{Conclusion}
In this paper we could clearly see the impact of platform-issues on the students performance in an exam-scenario and it's not that significant. There might still be certain aspect of long-term-effects,
which we couldn't simulate due to our circumstances, because there was a slight worsening happening when comparing our outcomes. It would be very interesting to see, how much significance such things like errors will show  in a long run with more variables included. \\\\
Don't neglect setting up your server properly and running it smoothly, so your students will thank you for that with better results (in short-term).

>>>>

\section{Discussion}
As we can see, the results show not much significance under our circumstances. Even though we cannot see a significance, we can see slight worsening of the average scores in the error groups than to the control group. But we don't have to forget, that this was a short term test (for example 1 hour exam) and we didn't include that many variables like time, age and so on. Having such problem-infected websites and platforms can be very frustrating in the long run and may make the decline of performance much worse, than we've seen here in our scenario of having to enter the 'exam' one time only.  Unfortunately, we couldn't recreate the long-term-scenario due to its complexity and sheer number of variables.          
\section{Conclusion}
In this paper we can clearly see the impact of platform-issues on the students performance in an exam-scenario and it's not that significant. There might still be certain aspect of long-term-effects,
which we couldn't simulate due to our circumstances, because there was a slight worsening happening when comparing our outcomes. It would be very interesting to see, how much significance such things like errors will show  in a long run with more variables included. \\\\
Don't neglect setting up your server properly and running it smoothly, so your students will thank you for that with better results (in short-term).
